Exposing Disputed Statements on the Web

### 2009-03-20 papers/uist_thinklink/thinklink.tex
Fixed position of top bar. Added ability to search wikipedia topics

Think Link builds on work in several different areas. The argumentation structure influenced by IBIS~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987}; the idea of highlighting information that may not be trustworthy was previously applied to Wikipedia by Wiki-Trust~\cite{Adler2008}; the model of using a community to collect and filter information from a range of sources is influenced by tagging systems~\cite{Marlow2006}; and the idea of gathering up a collection of snippets from web pages has been used by clipping tools such as Internet Scrapbook~\cite{Sugiura1998}.

@@

Think Link is an example of an Issue Based Information System (IBIS)~\cite{Rittel1973}. IBIS tools such as gIBIS~\cite{Conklin1987}, Compendium~\cite{Selvin2001}, Collabatorium~\cite{Klein2007}, Zeno~\cite{Gordon1996}, and Cohere~\cite{Shum2008} model discouse as a graph of connected ideas. While the graph structure varies between tools, most tools allow one to mark an idea as supporting or opposing another idea, and allow one to mark an idea as addressing an issue. Some tools, such as Collabatorium~\cite{Klein2007} and Cope It~\cite{Karacapilidis2001} structure an argument as a tree, while others such as Think Link, gIBIS~\cite{Conklin1987} and Cohere~\cite{Shum2008} structure an argument as a graph, in which a single idea can support or oppose multiple other ideas.

@@

Think Link uses a relatively simple graph structure, similar to that of gIBIS~\cite{Conklink1987}, allowing a claim to support, oppose, or be related to another claim. Cohere~\cite{Shum2008} extends this by allowing one to new link types marked with pro,con,or neutral polarity Toulmin~\cite{toulmin1958} proposes a more complex graph structure, implemented that expresses warrants, data, qualifiers, and reservations. Verheij~\cite{Verheij1999} uses the Toulmin model to create an argumentation tool for lawyers.

@@

Several tools layer an alternative navigation graph over information on the web. TextRunner~\cite{Etzioni2008} looks for instances of subject-verb-object triples on web pages and connects these together as a graph in which objects are linked by statements made about them on different web pages.

Kolak and Schillit~\cite{Kolak2008} detect cases where one book has quoted from another one, and use this to create links between books. This ``linking of quotations'' is similar in spirit to the linking of claims in Think Link.

@@

One of the goals of Think Link is that people should be able to browse information on the web through the ideas being expressed. This is a goal that is shared with several other projects. Kolak and Schilit~\cite{quotations} find places where a passage is repeated in several documents (usually a quotation) and allow users to navigate from such a passage to all other documents where that passage is quoted. Idea Navigation~\cite{ideanavigation} uses a natural language parser to identify subject-verb-object assertions in documents and then allows users to search for browse the assertions in a document corpus. ScentHighlights~\cite{Chi2005} identifies sections of text that you might find interesting and highlights them for you. ScentTrails~\cite{Olston2003} identifies links to documents that you might find interesting and makes them bigger. Unlike Think Link, these tool attempt to extract text of interest automatically, rather than relying on users to identify and connect interesting factual claims.

Much work has been done on the idea of using a graph to represent an argument~\cite{argumentation,argmas}. Popular argument models include the Toulmin Model~\cite{toulmin}, the Carneades Model~\cite{carneades}, and the IBIS model~\cite{ibis}. Models used for argumentation theory are usually significantly more complex than our simple supports/opposes model, with the result that they provide a more accurate model of the logical argument, at the cost of requiring more skill to assemble. One feature found in some argumentation graphs~\cite{Korb97acognitive} that we may add in the future is the ability to attach a numerical weight (maybe from voting) asserting how much a claim supports or opposes another claim, or how reliable a claim is.

>>>>

Think Link builds on work in several different areas. The argumentation structure influenced by IBIS~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}; the idea of highlighting information that may not be trustworthy was previously applied to Wikipedia by Wiki-Trust~\cite{Adler2008}; the model of using a community to collect and filter information from a range of sources is influenced by tagging systems~\cite{Marlow2006}; and the idea of gathering up a collection of snippets from web pages has been used by clipping tools such as Internet Scrapbook~\cite{Sugiura1998}.

@@

Think Link is an example of an Issue Based Information System (IBIS)~\cite{Rittel1973}. IBIS tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Collabatorium~\cite{Klein2007}, Zeno~\cite{Gordon1996}, and Cohere~\cite{Shum2008} model discouse as a graph of connected ideas. While the graph structure varies between tools, most tools allow one to mark an idea as supporting or opposing another idea, and allow one to mark an idea as addressing an issue. Some tools, such as Collabatorium~\cite{Klein2007} and Cope It~\cite{Karacapilidis2001} structure an argument as a tree, while others such as Think Link, gIBIS~\cite{Conklin1987a} and Cohere~\cite{Shum2008} structure an argument as a graph, in which a single idea can support or oppose multiple other ideas.

@@

Think Link uses a relatively simple graph structure, similar to that of gIBIS~\cite{Conklink1987a}, allowing a claim to support, oppose, or be related to another claim. Cohere~\cite{Shum2008} extends this by allowing one to new link types marked with pro,con,or neutral polarity Toulmin~\cite{toulmin1958} proposes a more complex graph structure, that expresses warrants, data, qualifiers, and reservations. Verheij~\cite{Verheij1999} uses the Toulmin model to create an argumentation tool for lawyers. More complicated models such as Carneades~\cite{Gordon2007} have been used for artificial intelligence, where it is necessary to be more precise about the structure of an argument.

@@

Several tools layer an alternative navigation graph over information on the web. TextRunner~\cite{Etzioni2008} and Idea Navigation~\cite{Etzioni2008} look for instances of subject-verb-object triples on web pages and connect these together as a graph in which objects are linked by statements made about them on different web pages. ScentHighlights~\cite{Chi2005a} highlights snippets of text on a web page that are related to topics that the user has said that they are intersted in. Kolak and Schillit~\cite{Kolak2008} detect cases where one book has quoted from another one, and use this to create links between books. This ``linking of quotations'' is similar in spirit to the linking of claims in Think Link.

@@
